### 2022-08-17 README.qmd
bleh

# AlgorithmicRecourseDynamics.jl - Research Paper 📝

>>>>

# AlgorithmicRecourseDynamics

<!-- [![Stable](https://img.shields.io/badge/docs-stable-blue.svg)](https://pat-alt.github.io/CounterfactualExplanations.jl/stable) -->
<!-- [![Dev](https://img.shields.io/badge/docs-dev-blue.svg)](https://pat-alt.github.io/CounterfactualExplanations.jl/dev) -->
[![Build Status](https://github.com/pat-alt/CounterfactualExplanations.jl/actions/workflows/CI.yml/badge.svg?branch=main)](https://github.com/pat-alt/CounterfactualExplanations.jl/actions/workflows/CI.yml?query=branch%3Amain)
<!-- [![Coverage](https://codecov.io/gh/pat-alt/CounterfactualExplanations.jl/branch/main/graph/badge.svg)](https://codecov.io/gh/pat-alt/CounterfactualExplanations.jl) -->

`AlgorithmicRecourseDynamics.jl` is a Julia package for modelling Algorithmic Recourse Dynamics.

## Research Paper 📝
